---
title: "C2 - Exercise Sheet"
description: |
  Here you find the exercise sheet for chapter 2: "Data Analysis Basics"
output:
  distill::distill_article:
    toc: true
    toc_depth: 3
    number_sections: false
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
solution = F
```


## Start a project and import data 
### Task 1
Create an R project for solving this Exercise Sheet. 

### Task 2
Download the csv-file [SSRC_data.csv](data/SSRC_data.csv) and the R script [SSRC_C2_template.R](templates/SSRC_C2_template.R) and put it in the R project folder you created in Task 1.

### Task 3 
Open the _SSRC_C2_template.R_ R Script.

### Task 4 
Use the _read.csv()_ command to load the SSRC data into R and call the respective data object _SSRC_data_.

```{r task4, include=solution}
# Load the dataset
SSRC_data <- read.csv("SSRC_data.csv")

```

### Task 5
Get a first impression of the dataset by checking out the first 6 rows of the dataset and by looking at the data in the spreadsheet mode.

```{r task5, include=solution}
# Check out the first 6 rows
head(SSRC_data)

# Produce spreadsheet mode
View(SSRC_data)


```

### Task 6
Install and load the _tidyverse_ package. 
(If you have already installed the package before, loading the package is sufficient)

```{r task6, include=solution}
# Install tidyverse package (if you have not done it yet)
# install.packages("tidyverse")

# Load tidyverse package
library("tidyverse")

```

## Isolating data 
### Task 7
Create a dataset that only contains the variables _age_ and _bmi_ and call this dataset _SSRC_data_C2_task_7_. Check out the first six rows of this dataset.

```{r task7, include=solution}
# Create the dataset 
SSRC_data_C2_task_7 <- select(SSRC_data, age, bmi)

# Check out dataset
head(SSRC_data_C2_task_7)

```

### Task 8
Create a dataset that only contains subjects with a bmi below 18.5 and call this dataset _SSRC_data_C2_task_8_. Check out the first six rows of this dataset.

```{r task8, include=solution}
# Create the dataset 
SSRC_data_C2_task_8 <- filter(SSRC_data, bmi < 18.5)

# Check out dataset
head(SSRC_data_C2_task_8)
```

### Task 9
Create a dataset that only contains individuals that have a low level of education and a bmi above 25 and call this dataset _SSRC_data_C2_task_9_. Check out the first six rows of this dataset.

```{r task9, include=solution}
# Create the dataset
SSRC_data_C2_task_9 <- filter(SSRC_data, education_level == "low" & bmi > 25)

# Check out dataset
head(SSRC_data_C2_task_9)
```

### Task 10
Create a dataset that only contains individuals with a bmi between 18.5 and 25 and is restricted to the variables _bmi_ and _gender_. Use the Pipe operator to do so and call the dataset _SSRC_data_C2_task_10_. Check out the first six rows of this dataset.

```{r task10, include=solution}
# Create the dataset 
SSRC_data_C2_task_10 <- SSRC_data %>% 
                        filter(bmi >= 18.5 & bmi <= 25) %>% 
                        select(bmi, gender)

# Check out dataset
head(SSRC_data_C2_task_10)
```

## Deriving information 

### Task 11
Use the summarize() command in combination with the filter() command to calculate the mean, maximum and minimum bmi of males that feature a low level of physical activity.

```{r task12, include=solution}
# Calculate mean, maximum and minimum bmi 
SSRC_data %>% 
  filter(gender == "male" & physical_activity_level == "low") %>% 
  summarize(mean_bmi = mean(bmi), maximum_bmi = max(bmi), minimum_bmi = min(bmi))
```

### Task 12
Use the summarize() command in combination with the group_by() command to compare males and females with respect to their mean age and bmi. 

```{r task13, include=solution}
# Compare males and females with respect to age and bmi 
SSRC_data %>% 
  group_by(gender) %>% 
  summarize(mean_bmi = mean(bmi), mean_age = mean(age))
```



